Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-08 Papers/ms.tex
Cauchy

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\

@@

>>>>

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\
$\mu_{\rm src}$ &	Expected mean flux of source blobs	& \\
$\mu_{\rm lens}$ &	Expected mean mass of lens blobs	& \\

@@

One might object to the Cauchy priors for the central positions on the
basis that they do not have rotational symmetry. However, the priors we
are assigning are prior to the values of the data pixel intensities only, and
not other facts about the data, such as its dimensions in arc seconds, or its
rectangular shape. Given these, there is no reason to insist on rotational
symmetry. The Cauchy priors are intended to enhance the plausibility that the
lens and source are somewhere near the centre of the image, but in a cautious
way.
